Reply To Examiners

### 2014-04-16 answer_thesis_examiner/chap1.tex
auto

\begin{align}
pdf(A_x) = \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}} \\
pdf(A) = \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}} \\
pdf(I) = \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}}
\end{align}

>>>>

\begin{align}
pdf(A_x) = \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}} \\
pdf(A) = \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}} \\
pdf(A_1) = 2A_1 e^{-A_1^2} \\
pdf(I) = \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}}
\end{align}

The integration of these becomes
\begin{align}
cdf(A_x) = \int_{-\infty}^{\infty} \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}}  \; \mathrm{d}A_x = \frac{1}{2} erf \left( \frac{A_x}{\sigma} \right)  \Big|_{-\infty}^{\infty} = 1 \\
cdf(A) = \int_0^{\infty} \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}}  \; \mathrm{d}A = -e^{-\frac{-A^2}{\sigma^2}} \Big|_0^{\infty} = 1\\
cdf(A_1) = \int_0^{\infty} 2A_1 e^{-A_1^2} \; \mathrm{d}A_1 = -e^{-A_1^2} \Big|_0^{\infty} = 1\\
cdf(I) = \int_0^{\infty} \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}} \; \mathrm{d}A_1 = -e^{-\frac{I}{\sigma^2}}  \Big|_0^{\infty} = 1
\end{align}
